dendro

### 2017-04-11 analysis/test-bai.Rmd
update script

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
```

@@

# sj 
sj <- read.rwl(fname=paste0(di, '/data/SNA_sanjuan.rwl'), format="tucson")
sjt <- read.rwl(fname=paste0(di, '/data/sj_test.rwl'), format="tucson")
```

@@

```{r} 
## BAI Function Piovesan

i <- "SNA0101"

bai_piovesan <- function(rwdf, diam_df){
  # rwdf: a ringwidth dataframe. row: years; col: id_cores
  # diam_df: a dataframe with diameter and id_core (two columns)

  # Output 
  bai <- rwdf

  # length years in Ring-width Data frame 
  vec_ly <- seq_len(nrow(rwdf))

  # ID cores 
  cores <- colnames(rwdf)

  for (i in cores){ 
    # 1 # Select core 
    id_core <- i

    # 2 # Select serie 
    rs <- rwdf[[id_core]]

    # 3 # Select diameter 
    dbh <- subset(diam_df, id_cores == id_core)
    dbh <- dbh[,2]

    # 4 # Prepare data to compute bai 
    #### Omit NA 
    rsomit <- na.omit(rs)

    #### Revert w 
    rs_rev <- rev(rsomit)

    # Cumsum rever w
    # cum_rs_rev <- cumsum(rs_rev)
    cum_rs_rev <- c(0, cumsum(rs_rev))

    # Compute d_{t} 
    d <- dbh - 2*cum_rs_rev

    # Remove last element 
    d <- d[-length(d)]

    # Bai
    b <- rev((pi/4) * ((d)^2 - (d - 2*rs_rev)^2))

    # Store BAI and NA 
    ### Which elements are NA? 
    na <- attributes(rsomit)$na.action
    ### Which ones no? 
    no_na <- vec_ly[!vec_ly %in% na]
    ### Put bai in those element with no NA
    bai[no_na, i] <- b 
  }
  bai 
}

# Test 
b_test_piovesan <- bai_piovesan(rwdf = sj_cor, diam_df = diam_cores_sj)
b_test_dplR <- bai.out(rwl = sj_cor, diam = diam_cores_sj)

@@

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
source(paste0(getwd(),"/script/R/bai_piovesan.R"))
```

@@

# sj 
sj <- read.rwl(fname=paste0(di, '/data_raw/dendro_ring/sn_sanjuan/sn_sanjuan.rwl'), format="tucson")

# canar 
ca <- read.rwl(fname=paste0(di, '/data_raw/dendro_ring/sn_canar/sn_canar.rwl'), format="tucson")
```

## Canar Data

@@

```{r} 
# Compute BAI for SJ locality 
baisj <- bai_piovesan(rwdf = sj_cor, diam_df = diam_cores_sj)
```

```{r}
rwl.report(sj_cor)

bai_p <- bai_piovesan(rwdf = sj_cor, diam_df = diam_cores_sj)
bai_d <- bai.out(rwl = sj_cor, diam = diam_cores_sj)

diam_cores_sjsin <- data.frame(id_cores = colnames(sj_sin),
                               dn_mm = colSums(sj_sin, na.rm = TRUE))
rownames(diam_cores_sjsin) <- NULL

bai_psin <- bai_piovesan(rwdf = sj_sin, diam_df = diam_cores_sjsin)
bai_dsinsin <- bai.out(rwl = sj_sin)
bai_dsin <- bai.out(rwl = sj_sin, diam = diam_cores_sjsin)

@@

```{r}

x <- c(1,2,2,3,1,3,4,5)

xx <- rollmean(x=x, k=3, align = 'center', na.pad = T)
